### 2016-09-08 ReviewComments/response.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Responses to Reviewer 3}
\textbf{3.1:} \emph{Though the implementation references Spark as the implementation
platform (as it also reflects in github repo provided), the algorithm design is
mostly limited to MapReduce, aka only Hadoop, which is a very small subset of
Spark. This may have a negative impact on the baseline implementation.
Particularly, recent releases of Spark have introduced window functions that can
be applied directly in the sliding window scenario here. Certainly, the algorithm
has to be redesigned to use DataFrame (and/or Spark SQL) interface, it has
been noted that this is a very efficient way to execute window functions in
Spark.}

\textbf{Response:} We thank the reviewer for the constructive comment.
% and carefully considered if applying the window-based function in the baseline algorithm is feasible.  
We do not implement TRPM using Spark-SQL in the original submission 
because the latest Spark at that time (i.e., version 1.6.2 released in June)
did not support \textit{user defined aggregate function} (UDAF) on the window operator\footnote{Window function improvements: \url{https://issues.apache.org/jira/browse/SPARK-7712}}. 
Without UDAF, we cannot integrate the Line Sweep Mining (Algorithm 1) with the window functions. 
During our revision period, Spark 2.0.0 is released with the support of UDAF. Thus, we make the exploration of implementing TRPM using Spark-SQL window functions.

Our Spark-SQL query for TRPM (referred to as TRPM-SQL) is constructed in three steps:
First, we reorganize the input to form a Dataset\footnote{In Spark 2.0.0, Dataset is used to replace DataFrame.} with two columns: ``Time'' and ``Clusters''. 
Second, we create a WindowSpec to represent the sliding window with size $\eta$ on the ``Time'' column.
Last, we apply the WindowSpec and our Line Sweep Mining Algorithm (as UDAF) on the input Dataset to
form the query.
%we call the window function in Spark-SQL with a UDAF representing our Line Sweep Algorithm. 
We compare the performance of TRPM-SQL with our original solutions in the following figure.
%
%Second, we extend the UDAF class to implement the Line Sweep Mining algorithm on the ``Clusters'' column. Third, we 
%create a WindowSpec to represent a sliding window with size $\eta$ on the ``Time'' column. We compare the performance
%of original Map-Reduce based TRPM (named TRPM-MR) with the TRMP-SQL in the following figure.

\begin{figure}[h]
\centering
\includegraphics[width=0.4\textwidth]{spark-sql-comp.eps}
\caption{Performance comparison with SPARE, TRPM and TRPM-SQL}
\end{figure}

The figure clearly shows that TRPM-SQL is inefficient with over
120 times slower than TRPM. After investigations on its query execution
plan, we find the slow performance of TRPM-SQL dues to the Spark-SQL Catalyst optimizer.
Since our TRPM-SQL query does not have a ``partition by'' clause, the Catalyst optimizer
treats the entire dataset as a SINGLE partition. Then it assigns the SINGLE partition to ONE executor,
which surrenders the parallel benefits of Spark system.
Due to the inefficiency of TRPM-SQL, in our revised version, we
still use the original Map-Reduce based TRPM for the performance comparisons.

%we found that Spark-SQL Catalyst optimizer assign the window query using only one
%executor. It is because that our TRPM-SQL query does not have a ``partition by'' clause, and
%the Catalyst optimizer treats the entire dataset as a SINGLE partition. Such a plan
%surrenders all the parallel benefits of the Spark system. 
% 
%
%
%To our surprise, such a window function based implementation DOES NOT perform well. The reason is that
%in TRPM, there is NO ``partition by'' clause. In such a case, Spark-SQL catalyst optimizer will treat
%the entire dataset as ONE big partition and run the UDAF for every window frame in ONE executor. We observe
%this from the physical query plan generated by Spark-Catalyst optimizer. This is no-doubt very inefficient,
%which results in a over 150 times slower than our current TRPM implementation. This performance
%of SPARE, TRPM-MR, TRPM-SQL for the three datasets are presented as follows:

### 2016-09-08 sec1_introduction.tex
Revise some minor points

A crucial task of data analysis on top of trajectories is 
to discover co-moving objects. A \emph{co-movement} pattern~\cite{li2013managing,zheng2015survey} 
refers to a group of objects traveling together for a certain period of time 
and the group is normally determined by their spatial proximity. 
A pattern is prominent if the size of the group exceeds $M$ and the length of the duration exceeds $K$, where $M$ and $K$ are parameters specified by users. Rooted from such a basic definition 
and driven by different mining applications, there are \revised{many} variants 
of co-movement patterns that have been developed with more advanced constraints.

Table~\ref{tbl:existing_co_patterns} summarizes several popular co-moving patterns 
with different constraints in the attributes of clustering in spatial proximity,
consecutiveness in temporal duration and computational complexity. 
In particular,  the \emph{flock}~\cite{gudmundsson2006flock} 
and the \emph{group}~\cite{wang2006grouppattern} patterns require 
all the objects in a group to be enclosed by a disk with radius $r$; 
whereas the \emph{convoy}~\cite{jeung2008convoy}, the \emph{swarm}~\cite{li2010swarm} 
and the \emph{platoon}~\cite{li2015platoon} patterns resort to density-based 
spatial clustering. 
In the temporal dimension, the \emph{flock}~\cite{gudmundsson2006flock} 
and the \emph{convoy}~\cite{jeung2008convoy} require all the timestamps 
of each detected spatial group to be consecutive, which is referred to as \emph{global consecutiveness}; 
whereas the \emph{swarm}~\cite{li2010swarm} does not impose any restriction. 
The \emph{group}~\cite{wang2006grouppattern} and the \emph{platoon}~\cite{li2015platoon} adopt a compromised manner by allowing
arbitrary gaps between the consecutive segments, which is called \emph{local consecutiveness}. 
They introduce a parameter $L$ to control the minimum length of each local consecutive segment.

@@

Figure~\ref{fig:related_work} is an example to demonstrate the concepts of various co-movement patterns. The trajectory database consists of six moving objects and the temporal dimension is discretized into six snapshots. In each snapshot, we treat the clustering method as a black-box and assume that they generate the same clusters. Objects in proximity are grouped in the dotted circles. As aforementioned, there are three parameters to determine the co-movement patterns and the default settings in this example are $M=2$, $K=3$ and $L=2$. Both the \emph{flock} and the \emph{convoy} require the spatial clusters to last for at least $K$ consecutive  timestamps. Hence,$\langle o_3,o_4:1,2,3 \rangle$ and $\langle o_5,o_6:3,4,5 \rangle$  remains the only two candidates matching the patterns. The \textit{swarm} relaxes the pattern matching by discarding the temporal consecutiveness constraint. Thus, it generates many more candidates than the \textit{flock} and the \textit{convoy}. The \textit{group} and the \textit{platoon} add another constraint on local consecutiveness to retain meaningful patterns. For instance, $\langle o_1,o_2:1,2,4,5 \rangle$ is a pattern matching local consecutiveness because timestamps $(1,2)$ and $(4,5)$ are two segments with length no smaller than $L=2$. The difference between the \textit{group} and the \textit{platoon} is that the \textit{platoon} has an additional parameter $K$ to specify the minimum number of snapshots for the spatial clusters. This explains why $\langle o_3,o_4,o_5:2,3 \rangle$ is a  \textit{group} pattern but not a \textit{platoon} pattern.

@@

\begin{table} \scriptsize
\centering
\begin{tabular}{|l|l|c|l|}
\hline 
\textbf{Pattern} & {\tiny \textbf{Proximity}} & {\tiny \textbf{Consecutiveness}} & {\tiny \textbf{Time Complexity}}\\ 
\hline 
flock~\cite{gudmundsson2004flock} & disk-based &  global & {\tiny $O(|\mathbb{O}||\mathbb{T}|\log(|\mathbb{O}|))$} \\ 
\hline 
convoy~\cite{jeung2008convoy} & density-based &   global & {\tiny $O(|\mathbb{O}|^2+|\mathbb{O}||\mathbb{T}|)$}\\ 
\hline 
swarm~\cite{li2010swarm} & density-based  & - & {\tiny $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$}  \\ 
\hline 
group~\cite{wang2006grouppattern} & disk-based &  local & {\tiny $O(|\mathbb{O}|^2|\mathbb{T}|)$}\\ 
\hline 
platoon~\cite{li2015platoon} & density-based &  local & {\tiny $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$}\\ 
\hline 
\end{tabular} 
\caption{Constraints and complexities of co-movement patterns. The time complexity indicates the performance wrt.
$|\mathbb{O}|$, $|\mathbb{T}|$ in the worst case, where $|\mathbb{O}|$ is the number of objects, and $|\mathbb{T}|$ is the number of discretized timestamps.}
\label{tbl:existing_co_patterns}
\end{table}
The other issue with existing methods is that they are built on top of centralized indexes which may not be scalable. Table~\ref{tbl:existing_co_patterns} shows their theoretical complexities in the worst cases and the largest real dataset ever evaluated in previous studies is up to million-scale points collected from hundreds of moving objects. In practice, the dataset is of much higher scale and the scalability of existing methods is left unknown. Thus, we conduct an experimental evaluation with $4000$ objects moving for $2500$ timestamps to examine the scalability. Results in Figure~\ref{fig:related_work_scalability} show that their performances degrade dramatically as the dataset scales up. For instance, the detection time of \emph{group} drops twenty times as the number of objects grows from \emph{1k} to \emph{4k}. Similarly,
the performance of \emph{swarm} drops over fifteen times as the number of snapshots grows from \emph{1k} to \emph{2.5k}.
These observations imply that existing methods are not scalable to support large-scale trajectory databases.

\begin{figure}[h]
	\vspace{-3mm}
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_O.eps}
		\subcaption{\small Varying No. of objects} 
    \label{fig:fig1}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_T.eps}
         \subcaption{\small Varying No. of timestamps}
    \label{fig:fig2}
    \end{subfigure}
    \vspace{-2mm}
    \caption{Performance measures on existing co-movement patterns. A sampled GeoLife dataset
    is used with up two 2.4 million data points. Default parameters are $M=15$, $K=180$, $L=30$.}
    \label{fig:related_work_scalability}
\end{figure}

Therefore, our primary contributions in this paper are to close these two gaps. 
First, we propose the \emph{general co-movement pattern} (GCMP) which models
various co-moment patterns in a unified way and can avoid 
the \emph{loose-connection} anomaly. In GCMP, we introduce a new gap parameter $G$ to pose a constraint on the temporal gap between two consecutive segments. 
%\revised{In GCMP, we adopt the concept of \emph{gap parameter $G$}
%in sequential pattern mining field~\cite{srikant1996mining} to constrain the temporal distance between two consecutive %segments.} 
By setting a feasible $G$, the loose-connection anomaly can be effectively controlled. In addition, our GCMP is also general. %and expressive. 
It can be reduced to any of the previous patterns by customizing its parameters.

Second, we investigate deploying our GCMP detector on MapReduce platforms (such as Hadoop and Spark) to tackle the scalability issue. Our technical contributions are three-fold. First, we design a baseline solution by replicating the snapshots in multiple data chunks to support effective parallel mining. Second, we devise a novel \emph{Star Partitioning and ApRiori Enumerator} (SPARE) framework to resolve limitations of the baseline. SPARE achieves workload balance by partitioning objects into fine granular stars.  For each star partition, an Apriori Enumerator is adopted to mine the co-movement patterns. Third, we leverage the \emph{temporal monotonicity} property of GCMP 
to design several optimization techniques including \emph{sequence simplification}, \emph{monotonicity pruning} and \emph{forward closure check} to further reduce the number of candidates enumerated in SPARE.

We conduct a set of extensive experiments on three large-scaled real datasets with hundreds of millions of
temporal points. 
The results show that both our parallel schemes efficiently support GCMP mining in large datasets.
In particular, with over 170 million trajectory points,
SPARE achieves upto 112 times speedup using 162 cores as compared to the state-of-the-art centralized schemes.
Moreover, SPARE further achieves upto 14 times efficiency
as compared to the baseline algorithm with almost linear scalability.

>>>>

A crucial task of data analysis on top of trajectories is 
to discover co-moving objects. A \emph{co-movement} pattern~\cite{li2013managing,zheng2015survey} 
refers to a group of objects traveling together for a certain period of time 
and the group is normally determined by their spatial proximity. 
A pattern is prominent if the size of the group exceeds $M$ and the length of the duration exceeds $K$, where $M$ and $K$ are parameters specified by users. Rooted from such a basic definition 
and driven by different mining applications, there are \revised{many} variants 
of co-movement patterns that have been developed with additional constraints.

Table~\ref{tbl:existing_co_patterns} summarizes several popular co-movement patterns 
with different constraints with respect to clustering in spatial proximity,
consecutiveness in temporal duration and computational complexity. 
In particular,  the \emph{flock}~\cite{gudmundsson2006flock} 
and the \emph{group}~\cite{wang2006grouppattern} patterns require 
all the objects in a group to be enclosed by a disk with radius $r$; 
whereas the \emph{convoy}~\cite{jeung2008convoy}, the \emph{swarm}~\cite{li2010swarm} 
and the \emph{platoon}~\cite{li2015platoon} patterns resort to density-based 
spatial clustering. 
In the temporal dimension, the \emph{flock}~\cite{gudmundsson2006flock} 
and the \emph{convoy}~\cite{jeung2008convoy} require all the timestamps 
of each detected spatial group to be consecutive, which is referred to as \emph{global consecutiveness}; 
whereas the \emph{swarm}~\cite{li2010swarm} does not impose any restriction. 
The \emph{group}~\cite{wang2006grouppattern} and the \emph{platoon}~\cite{li2015platoon} adopt a compromised approach by allowing
arbitrary gaps between consecutive segments, which is called \emph{local consecutiveness}. 
They introduce a parameter $L$ to control the minimum length of each local consecutive segment.

@@

\vspace{-2mm}
Figure~\ref{fig:related_work} is an example to demonstrate the concepts of the various co-movement patterns. The trajectory database consists of six moving objects and the temporal dimension is discretized into six snapshots. In each snapshot, we treat the clustering method as a blackbox and assume that they generate the same clusters. Objects in proximity are grouped in the dotted circles. As aforementioned, there are three parameters to determine the co-movement patterns and the default settings in this example are $M=2$, $K=3$ and $L=2$. Both the \emph{flock} and the \emph{convoy} require the spatial clusters to last for at least $K$ consecutive  timestamps. Hence,$\langle o_3,o_4:1,2,3 \rangle$ and $\langle o_5,o_6:3,4,5 \rangle$  are the only two candidates matching the patterns. The \textit{swarm} relaxes the pattern matching by discarding the temporal consecutiveness constraint. Thus, it generates many more candidates than the \textit{flock} and the \textit{convoy}. The \textit{group} and the \textit{platoon} add another constraint on local consecutiveness to retain meaningful patterns. For instance, $\langle o_1,o_2:1,2,4,5 \rangle$ is a pattern matching local consecutiveness because timestamps $(1,2)$ and $(4,5)$ are two segments with length no smaller than $L=2$. The difference between the \textit{group} and the \textit{platoon} is that the \textit{platoon} has an additional parameter $K$ to specify the minimum number of snapshots for the spatial clusters. This explains why $\langle o_3,o_4,o_5:2,3 \rangle$ is a  \textit{group} pattern but not a \textit{platoon} pattern.

@@

\begin{table}[t]
\centering
\begin{tabular}{|p{1.5cm}|p{1.5cm}|p{2cm}|p{2.3cm}|}
\hline 
\textbf{Pattern} & {\textbf{Proximity}} & { \textbf{Consecutive-ness}} & { \textbf{Time  Complexity}}\\ 
\hline 
flock~\cite{gudmundsson2004flock} & disk &  global & {$O(|\mathbb{O}||\mathbb{T}|\log(|\mathbb{O}|))$} \\ 
\hline 
convoy~\cite{jeung2008convoy} & density &   global & {$O(|\mathbb{O}|^2+|\mathbb{O}||\mathbb{T}|)$}\\ 
\hline 
swarm~\cite{li2010swarm} & density  & - & {$O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$}  \\ 
\hline 
group~\cite{wang2006grouppattern} & disk &  local & {$O(|\mathbb{O}|^2|\mathbb{T}|)$}\\ 
\hline 
platoon~\cite{li2015platoon} & density &  local & {$O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$}\\ 
\hline 
\end{tabular} 
\caption{Constraints and complexities of co-movement patterns. The time complexity indicates the performance wrt.
$|\mathbb{O}|$, $|\mathbb{T}|$ in the worst case, where $|\mathbb{O}|$ is the number of objects, and $|\mathbb{T}|$ is the number of discretized timestamps.}
\label{tbl:existing_co_patterns}
\end{table}

The other issue with existing methods is that they are built on top of centralized indexes which may not be scalable. Table~\ref{tbl:existing_co_patterns} shows their theoretical complexities in the worst cases and the largest real dataset ever evaluated in previous studies is up to million-scale points collected from hundreds of moving objects. In practice, the dataset is of much higher scale and the scalability of existing methods is left unknown. Thus, we conduct an experimental evaluation with $4000$ objects moving for $2500$ timestamps to examine the scalability. Results in Figure~\ref{fig:related_work_scalability} show that their performances degrade dramatically as the dataset scales up. For instance, the detection time of \emph{group} drops twenty times as the number of objects grows from \emph{1k} to \emph{4k}. Similarly,
the performance of \emph{swarm} drops over fifteen times as the number of snapshots grows from \emph{1k} to \emph{2.5k}.
These observations imply that existing methods are not scalable to support large-scale trajectory databases.

\begin{figure}[h]
	\vspace{-3mm}
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_O.eps}
		\subcaption{\small Varying No. of objects} 
    \label{fig:fig1}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_T.eps}
         \subcaption{\small Varying No. of timestamps}
    \label{fig:fig2}
    \end{subfigure}
    \vspace{-2mm}
    \caption{Performance measures on existing co-movement patterns. A sampled GeoLife dataset
    is used with upto 2.4 million data points. Default parameters are $M=15$, $K=180$, $L=30$.}
    \label{fig:related_work_scalability}
\end{figure}

Therefore, we aim to close these two gaps in this paper. 
First, we propose the \emph{general co-movement pattern} (GCMP) which models
various co-moment patterns in a unified way and can avoid 
the \emph{loose-connection} anomaly. In GCMP, we introduce a new gap parameter $G$ to pose a constraint on the temporal gap between two consecutive segments. 
%\revised{In GCMP, we adopt the concept of \emph{gap parameter $G$}
%in sequential pattern mining field~\cite{srikant1996mining} to constrain the temporal distance between two consecutive %segments.} 
By setting a feasible $G$, the loose-connection anomaly can be effectively controlled. In addition, our GCMP is also general. %and expressive. 
It can be reduced to any of the previous patterns by customizing its parameters.

Second, we investigate deploying our GCMP detector on the model MapReduce platform (i.e., Apache Spark) to tackle the scalability issue. Our technical contributions are three-fold. First, we design a baseline solution by replicating the snapshots in multiple data chunks to support effective parallel mining. Second, we devise a novel \emph{Star Partitioning and ApRiori Enumerator} (SPARE) framework to resolve limitations of the baseline. SPARE achieves workload balance by partitioning objects into fine granular stars.  For each star partition, an Apriori Enumerator is adopted to mine the co-movement patterns. Third, we leverage the \emph{temporal monotonicity} property of GCMP 
to design several optimization techniques including \emph{sequence simplification}, \emph{monotonicity pruning} and \emph{forward closure check} to further reduce the number of candidates enumerated in SPARE.

We conduct a set of extensive experiments on three large-scaled real datasets with hundreds of millions of
temporal points. 
The results show that both our parallel schemes efficiently support GCMP mining in large datasets.
In particular, with over 170 million trajectory points,
SPARE achieves upto 112 times speedup using 162 cores as compared to the state-of-the-art centralized schemes.
Moreover, SPARE further achieves almost linear scalability with upto 14 times efficiency
as compared to the baseline algorithm.

### 2016-09-08 sec3_definitions.tex
Revision
almost completed
Revise some minor points

\section{Definitions}
\label{sec:definition}
Let $\mathbb{O} = \{o_1 ,o_2,...,o_n\}$ be the set of objects and $\mathbb{T} =(1,2,...,N)$ be the discretized temporal dimension. A time sequence $T$ is defined as an ordered subset of $\mathbb{T}$. Given two time sequences $T_1$ and $T_2$, we define a bunch of commonly-used operators in this paper in Table~\ref{tbl:operators}.

\begin{table}[h] \scriptsize
\centering
\begin{tabular}{|c|l|}
\hline 
\textbf{Operator} & \textbf{Definition} \\ 
\hline
$T[i]$ & the $i$-th element in the sequence $T$ \\ 
\hline
$|T|$ & the number of elements in $T$\\
\hline
$\max(T)$ & the maximum element in $T$\\
\hline
$\min(T)$ & the minimum element in $T$\\
\hline
$\range(T)$ & the range of $T$, i.e., $\max(T) - \min(T) +1$\\ 
\hline 
$T[i:j]$ & subsequence of $T$ from $T[i]$ to $T[j]$ (inclusive) \\ 
\hline
$T_1\subseteq T_2$ &  $\forall T_1[x]\in T_1$, we have $T_1[x]\in T_2$. \\\hline
$T_3=T_1\cup T_2$ & $\forall T_3[x]\in T_3$, we have $T_3[x]\in T_1$ or $T_3[x] \in T_2$\\ 
\hline
$T_3=T_1\cap T_2$ & $\forall T_3[x]\in T_3$, we have $T_3[x]\in T_1$ and $T_3[x] \in T_2$\\ 
\hline
\end{tabular}
\caption{Operators on time sequence.} \label{tbl:operators}
\end{table}

We say a sequence $T$ is consecutive 
if $\forall i \in (1,...,|T|-1), T[i+1] = T[i] + 1$.  We refer each consecutive subsequence of $T$ as a \emph{segment}.
It is obvious that any time sequence $T$ can be decomposed into
segments and we say $T$ is \textit{L-consecutive}~\cite{li2015platoon} 
if the length of every segment is no smaller than $L$. As illustrated in Figure~\ref{fig:platoon_weakpoint}, patterns adopting the notion of $L$-consecutiveness (e.g., \emph{platoon} and \emph{group}) still suffer from the \emph{loose connection} problem. 
To avoid such an anomaly without losing pattern generality, we introduce a parameter $G$ to control the gaps between
timestamps in a pattern. Formally, a $G$-connected time sequence is defined as follows:

@@

Given a trajectory database that is discretized into snapshots, we can conduct a clustering method, either disk-based or density-based, to identify groups with spatial proximity. Let $T$ be the set of timestamps in which a group of objects $O$ are clustered. We are ready to define a more general co-movement pattern:
\begin{definition}[General Co-Movement Pattern]
A general co-movement pattern finds a set of objects $O$ satisfying the following five constraints: (1) \textbf{closeness:} the objects in $O$ belong to the same cluster in the timestamps of $T$; (2) \textbf{significance:} $|O| \geq M$; (3) \textbf{duration:} $|T| \geq K$; (4) \textbf{consecutiveness:} $T$ is $L$-consecutive; and (5) \textbf{connection:} $T$ is $G$-connected.
\end{definition}
There are four parameters in our general co-movement pattern, including object constraint $M$ and temporal constraints $K,L,G$.  By customizing these parameters, our pattern can 
express other patterns proposed in the previous literature, as illustrated in Table~\ref{tbl:patterns}. 
In particular, by setting $G=|\mathbb{T}|$, we achieve the \emph{platoon} pattern. By setting $G=|\mathbb{T}|,L=1$, we reach the \emph{swarm} pattern. By setting $G=|\mathbb{T}|$, $M=2$, $K=1$, we gain the \emph{group} pattern. Finally by setting $G=1$, we result in the \emph{convoy} and \emph{flock} patterns. 
In addition to the flexibility of representing other existing patterns, our GCMP is able to avoid the \emph{loose connection} anomaly by tuning the parameter $G$. 
It is notable that GCMP cannot be modeled by existing patterns. 
\begin{table}[h]
\centering
\begin{tabular}{|l|c|c|c|c|c|}
\hline 
\textbf{Pattern} & $M$ & $K$ & $L$ & $G$ & \textbf{Clustering} \\ 
\hline
Group & $2$ & $1$ & $2$ & $|\mathbb{T}|$ & Disk-based\\
\hline
Flock & $\cdot$ & $\cdot$ & $K$ & $1$ & Disk-based \\
\hline 
Convoy & $\cdot$ & $\cdot$ & $K$ & $1$ & Density-based\\ 
\hline 
Swarm & $\cdot$ & $\cdot$ & $1$ & $|\mathbb{T}|$ & Density-based \\ 
\hline 
Platoon & $\cdot$ & $\cdot$ & $\cdot$ & $|\mathbb{T}|$ & Density-based\\ 
\hline 
\end{tabular} 
\caption{Expressing other patterns using GCMP. $\cdot$ indicates a user specified value. $M$ represents the 
\emph{significance} constraint. $K$ represents the \emph{duration} constraint. $L$ represents the \emph{consecutiveness} constraint. $G$ represents the \emph{connection} constraint.}
\label{tbl:patterns}
\end{table}

Our definition of GCMP is independent of the clustering method. Users can apply different clustering methods to facilitate different application needs. 
We currently expose both disk-region based clustering and DBSCAN as options to the users. In summary, the goal of this paper is to present a parallel solution for discovering all the valid GCMPs from large-scale trajectory databases. Before we move on to the algorithmic part, we list the notations that are used in the following sections.

\begin{table}[h]\scriptsize
\centering
\begin{tabular}{|c|l|} 
\hline
\textbf{Symbol} & \textbf{Meaning} \\
\hline
$S_t$ & snapshot of objects at time $t$ \\
\hline
$M$ & significance constraint \\
\hline 
$K$ & duration constraint\\
\hline
$L$ & consecutiveness constraint\\
\hline
$G$ & connection constraint \\
\hline
$P=\langle O:T \rangle$ & pattern with object set $O$, time sequence $T$\\
\hline
%$C_t(o)$ & cluster of object $o$ at time $t$ \\
%\hline 
$S_t$ & set of clusters at snapshot $t$\\
\hline
$\eta$ & replication factor in the TRPM framework\\
\hline 
$\lambda_t$ & partition with snapshots $S_t,..,S_{t+\eta-1}$ \\
\hline
$G_A$ & aggregated graph in SPARE framework\\
\hline
$Sr_i $ &  star partition for object (vertex) $i$ \\
\hline 
$\Gamma$ & size of the largest star partition\\
\hline
\end{tabular} 
\caption{Summary of the use of notations.}
\end{table}

>>>>

\section{Definitions}
\label{sec:definition}
Let $\mathbb{O} = \{o_1 ,o_2,...,o_n\}$ be the set of objects and $\mathbb{T} =(1,2,...,N)$ be the discretized temporal dimension. A time sequence $T$ is defined as an ordered subset of $\mathbb{T}$. Given two time sequences $T_1$ and $T_2$, we define \revised{several} commonly-used operators in this paper in Table~\ref{tbl:operators}.

\begin{table}[h]
\vspace{-2mm}
\centering
\begin{tabular}{|c|l|}
\hline 
\textbf{Operator} & \textbf{Definition} \\ 
\hline
$T[i]$ & the $i$-th element in the sequence $T$ \\ 
\hline
$|T|$ & the number of elements in $T$\\
\hline
$\max(T)$ & the maximum element in $T$\\
\hline
$\min(T)$ & the minimum element in $T$\\
\hline
$\range(T)$ & the range of $T$, i.e., $\max(T) - \min(T) +1$\\ 
\hline 
$T[i:j]$ & subsequence of $T$ from $T[i]$ to $T[j]$ (inclusive) \\ 
\hline
$T_1\subseteq T_2$ &  $\forall T_1[x]\in T_1$, we have $T_1[x]\in T_2$. \\\hline
$T_3=T_1\cup T_2$ & $\forall T_3[x]\in T_3$, we have $T_3[x]\in T_1$ or $T_3[x] \in T_2$\\ 
\hline
$T_3=T_1\cap T_2$ & $\forall T_3[x]\in T_3$, we have $T_3[x]\in T_1$ and $T_3[x] \in T_2$\\ 
\hline
\end{tabular}
\caption{Operators on time sequence.} \label{tbl:operators}
\end{table}

\vspace{-3mm}
We say a sequence $T$ is consecutive 
if $\forall i \in (1,...,|T|-1), T[i+1] = T[i] + 1$.  We refer to each consecutive subsequence of $T$ as a \emph{segment}.
It is obvious that any time sequence $T$ can be decomposed into
segments and we say $T$ is \textit{L-consecutive}~\cite{li2015platoon} 
if the length of every segment is no smaller than $L$. As illustrated in Figure~\ref{fig:platoon_weakpoint}, patterns adopting the notion of $L$-consecutiveness (e.g., \emph{platoon} and \emph{group}) still suffer from the \emph{loose connection} anomaly. 
To avoid such an anomaly without losing generality, we introduce a parameter $G$ to control the gaps between
timestamps in a pattern. Formally, a $G$-connected time sequence is defined as follows:

@@

Given a trajectory database that is discretized into snapshots, we can conduct a clustering method, either disk-based or density-based, to identify groups with spatial proximity. Let $T$ be the set of timestamps in which a group of objects $O$ are clustered. We are ready to define a more general co-movement pattern:
\begin{definition}[General Co-Movement Pattern]
A general co-movement pattern finds a set of objects $O$ satisfying the following five constraints: (1) \textbf{closeness:} the objects in $O$ belong to the same cluster in the timestamps of $T$; (2) \textbf{significance:} $|O| \geq M$; (3) \textbf{duration:} $|T| \geq K$; (4) \textbf{consecutiveness:} $T$ is $L$-consecutive; and (5) \textbf{connection:} $T$ is $G$-connected.
\end{definition}
There are four parameters in our general co-movement pattern, including object constraint $M$ and temporal constraints $K,L,G$. 
%\revised{These parameters have different effects on the number of patterns discovered. Larger $K$, $L$, $M$ 
%put more stringent constraints on patterns such that less patterns could satisfy the requirements. Larger $G$
%relaxes the temporal constraints therefore more patterns could be discovered. Currently, we leave tuning of
%parameters to users to accommodate various application needs.}  
By customizing these parameters, our pattern can 
express other patterns proposed in the literature, as illustrated in Table~\ref{tbl:patterns}. 
In particular, by setting $G=|\mathbb{T}|$, we achieve the \emph{platoon} pattern. By setting $G=|\mathbb{T}|,L=1$, we reach the \emph{swarm} pattern. By setting $G=|\mathbb{T}|$, $M=2$, $K=1$, we gain the \emph{group} pattern. Finally by setting $G=1$, we result in the \emph{convoy} and \emph{flock} patterns. 
In addition to the flexibility of representing other existing patterns, our GCMP is able to avoid the \emph{loose connection} anomaly by tuning the parameter $G$. 
%It is notable that GCMP cannot be modeled by existing patterns. 
\begin{table}[h]
\centering
\begin{tabular}{|l|c|c|c|c|c|}
\hline 
\textbf{Pattern} & $M$ & $K$ & $L$ & $G$ & \textbf{Clustering} \\ 
\hline
Group & $2$ & $1$ & $2$ & $|\mathbb{T}|$ & disk\\
\hline
Flock & $\cdot$ & $\cdot$ & $K$ & $1$ & disk \\
\hline 
Convoy & $\cdot$ & $\cdot$ & $K$ & $1$ & density\\ 
\hline 
Swarm & $\cdot$ & $\cdot$ & $1$ & $|\mathbb{T}|$ & density\\ 
\hline 
Platoon & $\cdot$ & $\cdot$ & $\cdot$ & $|\mathbb{T}|$ & density\\  
\hline 
\end{tabular} 
\caption{Expressing other patterns using GCMP. $\cdot$ indicates a user specified value.
% $M$ represents the  \emph{significance} constraint. $K$ represents the \emph{duration} constraint. $L$ represents the \emph{consecutiveness} constraint. $G$ represents the \emph{connection} constraint.
}
\label{tbl:patterns}
\end{table}

\vspace{-2mm}
Our definition of GCMP is independent of the clustering method. Users can apply different clustering methods to facilitate different application needs. 
We currently expose both disk-region based clustering and DBSCAN as options to the users. In summary, the goal of this paper is to present a parallel solution for discovering all the valid GCMPs from large-scale trajectory databases. Before we move on to the algorithmic part, we list the notations that are used in the following sections.

\begin{table}[h]
\centering
\begin{tabular}{|c|l|} 
\hline
\textbf{Symbol} & \textbf{Meaning} \\
\hline
$S_t$ & snapshot of objects at time $t$ \\
\hline
$M$ & significance constraint \\
\hline 
$K$ & duration constraint\\
\hline
$L$ & consecutiveness constraint\\
\hline
$G$ & connection constraint \\
\hline
$P=\langle O:T \rangle$ & pattern with object set $O$, time sequence $T$\\
\hline
%$C_t(o)$ & cluster of object $o$ at time $t$ \\
%\hline 
$S_t$ & set of clusters at snapshot $t$\\
\hline
$\eta$ & replication factor in the TRPM framework\\
\hline 
$\lambda_t$ & partition with snapshots $S_t,..,S_{t+\eta-1}$ \\
\hline
$G_A$ & aggregated graph in SPARE framework\\
\hline
$Sr_i $ &  star partition for object (vertex) $i$ \\
\hline 
$\Gamma$ & size of the largest star partition\\
\hline
\end{tabular} 
\caption{Summary of the use of notations.}
\end{table}
